County Figures

### 2023-06-25 reports/county_figures.Rmd
concordance w/ covidestim figure

w_data <- wjoined %>% 
  select(-date) %>%
  distinct() %>%
  filter(fips %in% counties_with_waste) %>%
  filter(!is.na(mean_conc)) %>%
  group_by(fips, version) %>%
  mutate(mean_conc_std = (mean_conc - mean(mean_conc))/ 
           sd(mean_conc),
         exp_cases_median_std = (exp_cases_median -
                                   mean(exp_cases_median)/sd(exp_cases_median)),
         infections_std = (infections - mean(infections))/sd(infections),
         exp_cases_lb_std = (exp_cases_lb - mean(exp_cases_lb)/ sd(exp_cases_lb)),
        exp_cases_ub_std = (exp_cases_ub - mean(exp_cases_ub)/ sd(exp_cases_ub)),
         positive_std = (positive - mean(positive))/sd(positive))  %>%
  ungroup()

@@

@@

@@

@@

ma_concordance_by_county %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value")

##############################################
# stacked bar chart of concordance by county
##############################################
ma_concordance_by_county %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value") %>%
  group_by(county_name) %>%
  mutate(m = prop[which(in_interval=="In Interval")]) %>%
  ungroup() %>%
  mutate(in_interval = factor(in_interval, levels = c("Above Interval",
                            "In Interval", "Below Interval"))) %>%
  ggplot(aes(x= fct_reorder(county_name,m), 
             fill = (in_interval), y =prop)) + 
  geom_bar(stat="identity",position="stack") +
  theme_c() +
  coord_flip()+
  scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Massachusetts: Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = TeX("For Implementation with $P(S_1|untested)$ Centered at Survey Value")) +
  theme_c() +
  theme(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1))

@@

in_interval <- ma_concordance %>%
  filter(in_interval == "In Interval") %>%
  mutate(n_interval = n_per_version) %>%
  select(vlabel, n_interval)

@@

>>>>

w_data <- wjoined %>% 
  select(-date) %>%
  distinct() %>%
  filter(fips %in% counties_with_waste) %>%
  filter(!is.na(mean_conc)) %>%
  group_by(fips, version) %>%
  mutate(
    mean_conc_std = (mean_conc - mean(mean_conc))/ 
           sd(mean_conc),
    exp_cases_median_std = (exp_cases_median -  mean(exp_cases_median))/
                                   sd(exp_cases_median),
         infections_std = (infections - mean(infections))/
      sd(infections),
         exp_cases_lb_std = (exp_cases_lb - mean(exp_cases_lb))/
      sd(exp_cases_lb),
        exp_cases_ub_std = (exp_cases_ub - mean(exp_cases_ub))/
      sd(exp_cases_ub),
         positive_std = (positive - mean(positive))
    /sd(positive))  %>%
  ungroup()

@@

covidestim_correlations <- w_data %>%
  filter(!is.na(infections_std)) %>%
  group_by(vlabel) %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(exp_cases_median_std,infections_std,
                              use = "complete.obs")) %>%
  mutate(x=2.5,
         y=.1)

@@

wjoined <- wjoined %>%
  mutate(name = gsub("County, MA","", name))

@@

ma_concordance_by_county <- wjoined %>%
  filter(biweek >=6) %>%
  # covidestim does not report estimates for Nantucket 
  filter(!grepl("Nantucket", name )) %>%
  select(-date) %>%
  mutate(name = gsub("$", "", 
                            name, fixed=TRUE)) %>%
  select(exp_cases_lb, exp_cases_ub, 
         name, biweek, vlabel, infections) %>%
   distinct() %>%
  mutate(in_interval = case_when(
    exp_cases_lb <= infections & 
      infections <= exp_cases_ub ~ "In Interval",
    exp_cases_lb  > infections  ~ "Below Interval",
    exp_cases_ub < infections ~ "Above Interval"
  ) ) %>%
  group_by(in_interval, name, vlabel) %>%
  summarize(n_per_county=n()) %>%
  group_by(name,vlabel) %>%
  mutate(total = sum(n_per_county),
         prop = n_per_county/total) %>%
  mutate(state="MA") %>%
  ungroup()

@@

##############################################
# stacked bar chart of concordance by county
##############################################
ma_concordance_by_county %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value") %>%
  group_by(name) %>%
  mutate(m = prop[which(in_interval=="In Interval")]) %>%
  ungroup() %>%
  mutate(in_interval = factor(in_interval, levels = c("Above Interval",
                            "In Interval", "Below Interval"))) %>%
  ggplot(aes(x= fct_reorder(name,m), 
             fill = (in_interval), y =prop)) + 
  geom_bar(stat="identity",position="stack") +
  theme_c() +
  coord_flip()+
  scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Massachusetts: Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = TeX("For Implementation with $P(S_1|untested)$ Centered at Survey Value")) +
  theme_c() +
  theme(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1))

@@

```{r, fig.width=15}

# 
in_interval <- ma_concordance %>%
  filter(in_interval == "In Interval") %>%
  mutate(n_interval = n_per_version) %>%
  select(vlabel, n_interval)

@@

ma_concordance %>%
  group_by(vlabel) %>%
  mutate(total=sum(n_per_version)) %>%
  filter(in_interval == "In Interval") %>%
  mutate(n_interval = n_per_version) %>%
  ggplot(aes(y=fct_reorder(vlabel,prop), x=prop)) +
  geom_text(aes(label=round(prop,3), x= prop+.03), 
             angle=0) +
  geom_bar(stat="identity", fill="#596281") +
  scale_y_discrete(breaks= unique(ma_concordance$vlabel),
                   labels=function(x)TeX(x)) +
  scale_x_continuous(expand=c(0,0), 
                     limits=c(0,.9), n.breaks=7)  +
  theme_c() +
  labs(y="",
       x="Proportion Containing the Covidestim Median",
       title="Proportion Containing the Covidestim Median\nBy Implementation")
